---
title: "UCI Wine Quality"
author: "pshyamku-courses"
date: '9/13/2020'
output: 
  ioslides_presentation: 
    smaller: yes
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
	warning = FALSE,
	cache = TRUE,
	tidy = TRUE,
	tidy.opts = list(width.cutoff = 60))
```

## Objectives {.smaller}

- Create a web page presentation using R Markdown that features a plot created with Plotly. 
- Host your webpage on either GitHub Pages, RPubs, or NeoCities. 
- The webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

**Chosen Data Source**

We will be exploring the wine quality data set from the UCI Machine Learning Repository <http://archive.ics.uci.edu/ml/datasets/Wine+Quality>
Two datasets are included. They are related to red and white variants of the Portuguese "Vinho Verde" wine. 

*References*
P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis.
Modeling wine preferences by data mining from physicochemical properties. In Decision Support Systems, Elsevier, 47(4):547-553, 2009.

## Data Attribute Information: {.smaller}
**Input variables (based on physicochemical tests):**

- fixed acidity, volatile acidity, citric acid
- residual sugar
- chlorides
- free sulfur dioxide, total sulfur dioxide
- density
- pH
- sulphates
- alcohol

**Output variable (based on sensory data):**

- quality (score between 0 and 10)

Lets load the Red wine data
```{r echo = FALSE, results='hide', }
suppressWarnings(library(plotly, verbose = FALSE))
suppressWarnings(library(ggplot2, verbose = FALSE))
```
```{r echo = TRUE}
red_wine <- read.csv(file = './Data/winequality-red.csv', header = TRUE, sep = ';')
```

## R Code to generate plots {.smaller}
We will explore a small subset of attributes and the impact on quality of the wine.

```{r wine, echo = TRUE}
q1 <- ggplotly(ggplot(data = red_wine, 
                      aes(x = sulphates, y = pH, color = quality)) +
                 geom_point() +
  scale_color_gradientn(colours = rainbow(5)) + 
  labs( x = "Sulphates", y = "pH", color = "Quality Rating")) 
q2 <- ggplotly(ggplot(data = red_wine, 
                      aes(x = residual.sugar, y = citric.acid, color = quality)) + 
                 geom_point() +
  scale_color_gradientn(colours = rainbow(5)) + 
  labs( x = "Residual Sugar", y = "Cirtic Acid", color = "Quality Rating"))
q3 <- ggplotly(ggplot(data = red_wine, 
                      aes(x = chlorides, y = total.sulfur.dioxide,
                          color = quality)) +
                 geom_point() +
  scale_color_gradientn(colours = rainbow(5)) + 
  labs( x = "Chlorides", y = "Total Sulfur Dioxide", color = "Quality Rating"))
q4 <- ggplotly(ggplot(data = red_wine, 
                      aes(x = alcohol, y = density, color = quality)) + 
                 geom_point() +
  scale_color_gradientn(colours = rainbow(5))+ 
  labs( x = "Alcohol content", y = "Density", color = "Quality Rating"))
```

## Interactive Plot {.smaller}

```{r echo=TRUE, fig.align='center'}
subplot(q1,q2,q3,q4, titleX = TRUE, titleY = TRUE, nrows = 2, margin = 0.07)
```

